---
title: "APS606 R Assignment 4"
author: "Your Name"
date: "8/24/2020"
output: 
  html_document:
    theme: united
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Assignment 4

* In this assignment, we are going to apply some of the build in data set in R for descriptive statistics analysis.
* To earn full grade in this assignment, students need to complete the coding tasks for each question to get the result.
* After finished all the questions, knit the document into HTML format for submission.

### Question 1

In this exercise, we will examine the **happy** data in the data folder. We will attempt to model **happiness** (happiness of the population) in 191 countries based on an independent variable.

```{r, echo=FALSE}
library(readr)
happy <- read_csv("data/happiness.csv")
happy <- happy[c("country_name", "population", "year", "gdp", "gdpPerCap", "gini", "happiness")]
happy <- na.omit(happy)

head(happy)
```

a. Create the descriptive summary for the data set, **happy**.

```{r}
# Enter your code here!


```

b. Create a pairs plot to display the correlations between all variables.  Can you make a good judgement which variable correlated with **happiness** the most?

```{r}
# Enter your code here!


```

Ans: 

c. Use the correlation function to calculate the correlation between all the variables in the data set. Which variable has the highest correlation to **happiness** (in absolute value)?

```{r}
# Enter your code here!
cor(happy[-c(1)])
mean(happy$gdpPerCap)
```

Ans: 

d. According to **part c**, use the variable you found to fit the simple linear regression and print the summary output of the model. Hint: the dependent variable is **happiness** and the independent variable is your answer in part c. 

```{r}
# Enter your code here!
  
  
```


e. According to the model summary output, conclude three facts about the model. Hint: it could be the test of the coefficient, interpreting the $R^2$, test of the model, marginal effect of the independent variable, etc.

Ans:


***

### Question 2

Applying the same data set, let's try to answer the following questions.

a. Use the model in **Question 1, part d**, predict the **happiness** given the gdpPerCap is 10000, 15000, and 20000.

```{r}
# Enter your code here!


```


b. Create a 95% confidence interval for your prediction in **part a**.

```{r}
# Enter your code here!


```


c. Create a scatter plot for **happyiness** and the independent variable in your model, then plot the fitted model line to the graph. Hint: the independent should always be on the x-axis and the fitted line is using the abline() function in R.

```{r}
# Enter your code here!


```


d. Is there any way we can increase the explanatory power of the linear model? If yes, what would you suggest doing to improve the model fit? You can provide your code to proof your suggestion, but it is optional!!

Ans:

```{r}
# Enter your code here!
  

```

