---
title: "APS606 R Assignment 2"
author: "Your Name"
date: "8/24/2020"
output: 
  html_document:
    theme: united
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Assignment 2

* In this assignment, we are going to apply some of the build in data set in R for descriptive statistics analysis.
* To earn full grade in this assignment, students need to complete the coding tasks for each question to get the result.
* After finished all the questions, knit the document into HTML format for submission.

### Question 1

Given the simulated normally distributed data. Answer the following questions with your code.

a. Plot a histogram to show the distribution of the simulated data.

b. Assign the mean of the data set to **m** and standard deviation to **sd**.

c. Find the probability for randomly select a score **below 100** from this simulated data. P(X<100)

d. Find the probability for randomly select a score **above 150** from this simulated data. P(X>150)

e. Find the probability for randomly select a score **between 110 and 130** from this simulated data. P(110<X<130)

f. What is the score that is at the **90th percentile** of this data? P(X < x) = 0.9

```{r}
# Simulate a normally distributed data set
n <- rnorm(10000, mean = 120, sd = 12)

# Enter your code here!
# Part a



# Part b



# Part c



print(paste("The probability to randomly select a score below 100 is ", ))

# Part d



print(paste("The probability to randomly select a score above 150 is ", ))

# Part e



print(paste("The probability to randomly select a score between 110 and 130 is ", ))

# Part f



print(paste("The score that is at 90th percentile in the data set is ", ))

```


### Question 2

Suppose we are randomly selecting 20 students in 100 South East Asia regions for an interview about their family status and education opportunity. Given the historical success rate for student entering college is about 30% in these regions.  Answer the following question about this random sample selection process based on the simulated data.

a. Plot a histogram to show the distribution of the simulated data.

b. Print the mean and sd of the simulated data. 

c. What type of the distribution do we call this?  According to the histogram, what is the shape of the distribution? (Skew to the left, skew to the right, or center in the middle) 

d. What is the probability that 5 out of the 20 students in the interview would go to college? P(X = 5)

e. What is the probability that 3 or less of the 20 students in the interview would go to college? P(X <= 3)

f. What is the probability that 8 or more of the 20 students in the interview would go to college? P(X >= 20)

g. What is the number of students in the 20 students interview would yield the 80th percentile from the sample selection? P(X < x) = 0.80


```{r}
n <- rbinom(100, 20, 0.3)

# Enter your code here!
# Part a


# Part b


# Part c

print("This distribution is called ______________ and the shape of the data distribution of the defective computer is ________________")


# Part d


print(paste("The probability that 5 out of the 20 students in the interview would go to college is ", ))

# Part e


print(paste("The probability that 3 or less out of the 20 students in the interview would go to college is ", ))

# Part f


print(paste("The probability that 8 or more out of the 20 students in the interview would go to college is ", ))

# Part g


print(paste("There is a 80% chance to find ",  , " or less student in the 20 students interview would go to college."))


```
